```{r echo = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

# stubs {#webmockr-stubs}

```{r}
library("webmockr")
```

set return objects

```{r}
stub_request("get", "https://httpbin.org/get") %>%
  wi_th(
    query = list(hello = "world")) %>%
    to_return(status = 418)
```

```{r}
x$get('get', query = list(hello = "world"))
```

**Stubbing requests based on method, uri and query params**

```{r}
stub_request("get", "https://httpbin.org/get") %>%
  wi_th(query = list(hello = "world"), 
        headers = list('User-Agent' = 'libcurl/7.51.0 r-curl/2.6 crul/0.3.6', 
                       'Accept-Encoding' = "gzip, deflate"))
```

```{r}
stub_registry()
```

```{r}
x <- HttpClient$new(url = "https://httpbin.org")
x$get('get', query = list(hello = "world"))
```

**Stubbing requests and set expectation of a timeout**

```{r eval=FALSE}
stub_request("post", "https://httpbin.org/post") %>% to_timeout()
x <- HttpClient$new(url = "https://httpbin.org")
x$post('post')
#> Error: Request Timeout (HTTP 408).
#>  - The client did not produce a request within the time that the server was prepared
#>    to wait. The client MAY repeat the request without modifications at any later time.
```

**Stubbing requests and set HTTP error expectation**

```{r eval=FALSE}
library(fauxpas)
stub_request("get", "https://httpbin.org/get?a=b") %>% to_raise(HTTPBadRequest)
x <- HttpClient$new(url = "https://httpbin.org")
x$get('get', query = list(a = "b"))
#> Error: Bad Request (HTTP 400).
#>  - The request could not be understood by the server due to malformed syntax.
#>    The client SHOULD NOT repeat the request without modifications.
```

## Writing to disk {#webmockr-disk}


There are two ways to deal with mocking writing to disk. First, you can create a file
with the data you'd like in that file, then tell crul or httr where that file is.
Second, you can simply give webmockr a file path (that doesn't exist yet) and some 
data, and webmockr can take care of putting the data in the file.


```{r echo=FALSE}
stub_registry_clear()
request_registry_clear()
```

Here's the first method, where you put data in a file as your mock, then pass the 
file as a connection (with `file(<file path>)`) to `to_return()`.

```{r}
## make a temp file
f <- tempfile(fileext = ".json")
## write something to the file
cat("{\"hello\":\"world\"}\n", file = f)
## make the stub
invisible(stub_request("get", "https://httpbin.org/get") %>% 
  to_return(body = file(f)))
## make a request
out <- HttpClient$new("https://httpbin.org/get")$get(disk = f)
## view stubbed file content
readLines(file(f))
```

With the second method, use `webmockr::mock_file()` to have `webmockr` handle file
and contents.

```{r}
g <- tempfile(fileext = ".json")
## make the stub
invisible(stub_request("get", "https://httpbin.org/get?a=b") %>% 
  to_return(body = mock_file(path = g, payload = "{\"hello\":\"mars\"}\n")))
## make a request
out <- crul::HttpClient$new("https://httpbin.org/get?a=b")$get(disk = g)
## view stubbed file content
readLines(out$content)
```

`webmockr` also supports `httr::write_disk()`, here letting `webmockr` handle the
mock file creation:

```{r}
library(httr)
httr_mock()
## make a temp file
f <- tempfile(fileext = ".json")
## make the stub
invisible(stub_request("get", "https://httpbin.org/get?cheese=swiss") %>% 
  to_return(
    body = mock_file(path = f, payload = "{\"foo\": \"bar\"}"),
    headers = list('content-type' = "application/json")
  ))
## make a request
out <- GET("https://httpbin.org/get?cheese=swiss", write_disk(f, TRUE))
## view stubbed file content
readLines(out$content)
```

```{r cleanup, echo=FALSE}
unlink(c(f, g))
httr_mock(FALSE)
```
