#  (PART) vcr {-}

# Caching HTTP requests {#vcr-intro}

Record HTTP calls and replay them

## Package documentation {#vcr-pkgdown}

Check out <https://docs.ropensci.org/vcr/> for documentation on `vcr` functions.

## Terminology {#terminology}

```{r, results = "asis", echo=FALSE}
get_vcr_doc("man/rmdhunks/glossary.Rmd")
```


## Basic usage {#vcr-basic-usage}

```{r, results = "asis", echo=FALSE}
get_vcr_doc("man/rmdhunks/basic-usage.Rmd")
```

All components of both the request and response are preserved, so that the HTTP client (in this case `crul`) can reconstruct its own response just as it would if it wasn't using `vcr`.

## vcr enabled testing {#vcr-enabled-testing}

### check vs. test {#check-vs-test}

> TLDR: Run `devtools::test()` before running `devtools::check()` for recording your cassettes.

When running tests or checks of your whole package, note that you'll get different results with
`devtools::check()` (check button of RStudio build pane) vs. `devtools::test()` (test button of RStudio build pane). This arises because `devtools::check()` runs in a
temporary directory and files created (vcr cassettes) are only in that temporary directory and
thus don't persist after `devtools::check()` exits. 

However, `devtools::test()` does not run in a temporary directory, so files created (vcr
cassettes) are in whatever directory you're running it in.

Alternatively, you can run `devtools::test_file()` (or the "Run test" button in RStudio) to create your vcr cassettes one test file at a time. 


### CI sites: Travis, Appveyor, etc. {#vcr-ci}

Similar considerations are involved when dealing with Travis, Appveyor, Circle-CI,
etc. 

There are a few differences. With CI services you can manage environment variables
so you can run tests that require API keys, etc. In addition, if tests fail you
aren't threatened with your package being taken down.


