#  (PART) vcr {-}

# Caching HTTP requests {#vcr-intro}

some intro text ...

## Package documentation {#vcr-pkgdown}

Check out <https://ropensci.github.io/vcr/> for documentation on `vcr` functions.

## Terminology {#terminology}

* **http**: [hyptertext transfer protocol](https://en.wikipedia.org/wiki/Hypertext_Transfer_Protocol)
* **vcr**: the name comes from the idea that we want to record something and play it back later, like a [VCR](https://en.wikipedia.org/wiki/Videocassette_recorder)
* **cassette**: A _thing_ to record HTTP interactions to. Right now the only option is file system, but in the future could be other things, e.g. a key-value store like [Redis](https://redis.io/)
* **Persister**: defines how to save requests - currently only option is the file system
* **Serializers**: defines how to serialize the HTTP response; that is, how the data is stored on whatever the persister is (right now only file system). Currently only option is YAML; other options in the future could include e.g. JSON
* **insert cassette**: create a cassette (all HTTP interactions will be recorded to this cassette). once a cassette is inserted, we don't allow insertion of additional cassettes
* **eject cassette**: eject the cassette (no longer recording to that cassette). however, if any interactions were written to disk, those are still stored there
* **replay**: refers to using a cached result of an http request that was recorded earlier
* **recording**: this means you've set vcr in a mode in which we can record HTTP interactions. sometimes recording can be not possible given user configuration or otherwise

## Basic usage {#basic-usage}

```{r echo=FALSE}
suppressPackageStartupMessages(require(vcr, quietly = TRUE))
unlink(file.path(cassette_path(), "helloworld.yml"))
```

```{r collapse=TRUE, messages=FALSE}
library(vcr)
library(crul)

cli <- crul::HttpClient$new(url = "https://api.crossref.org")
system.time(
  use_cassette(name = "helloworld", {
    cli$get("works", query = list(rows = 3))
  })
)
```

The request gets recorded, and all subsequent requests of the same form used the cached HTTP response, and so are much faster

```{r collapse=TRUE, messages=FALSE}
system.time(
  use_cassette(name = "helloworld", {
    cli$get("works", query = list(rows = 3))
  })
)
```

```{r echo=FALSE}
unlink(file.path(cassette_path(), "helloworld.yml"))
```

Importantly, your unit test deals with the same inputs and the same outputs - but behind the scenes you use a cached HTTP resonse - thus, your tests run faster.

The cached response looks something like (condensed for brevity):

```yaml
http_interactions:
- request:
    method: get
    uri: https://api.crossref.org/works?rows=3
    body:
      encoding: ''
      string: ''
    headers:
      User-Agent: libcurl/7.54.0 r-curl/3.2 crul/0.5.2
      Accept-Encoding: gzip, deflate
      Accept: application/json, text/xml, application/xml, */*
  response:
    status:
      status_code: '200'
      message: OK
      explanation: Request fulfilled, document follows
    headers:
      status: HTTP/1.1 200 OK
      content-type: application/json;charset=UTF-8
      vary: Accept
      access-control-allow-origin: '*'
      access-control-allow-headers: X-Requested-With
      content-length: '5360'
      server: http-kit
      date: Sat, 28 Apr 2018 15:12:29 GMT
      x-rate-limit-limit: '50'
      x-rate-limit-interval: 1s
      connection: close
    body:
      encoding: UTF-8
      string: '{"status":"ok","message-type":"work-list","message-version":"1.0.0","message":{"facets":{},"total-results":96454147,"items":[{"indexed":{"date-parts":[[2017,10,23]],"date-time":"2017-10-23T19:27:25Z","timestamp":1508786845330},"reference-count":0,"publisher":"Elsevier
        BV","issue":"3","license":[{"URL":"http:\/\/www.elsevier.com\/tdm\/userlicense\/1.0\/","start":{"date-parts":[[1999,10,1]],"date-time":"1999-10-01T00:00:00Z","timestamp":938736000000},"delay-in-days":0,"content-version":"tdm"}],"content-domain":{"domain":[],"crossmark-restriction":false},"short-container-title":["Progress
        in Planning"],"published-print":{"date-parts":[[1999,10]]},"DOI":"10.1016\/s0305-9006(99)00007-0","type":"journal-article","created":{"date-parts":[[2002,7,26]],"date-time":"2002-07-26T00:11:38Z","timestamp":1027642298000},"page":"vii","source":"Crossref","is-referenced-by-count":0,"title":["Editorial"],"prefix":"10.1016","volume":"52","member":"78","container-title":["Progress
        in Planning"],"link":[{"URL":"http:\/\/api.elsevier.com\/content\/article\/PII:S0305900699000070?httpAccept=text\/xml","content-type":"text\/xml","content-version":"vor","intended-application":"text-mining"},{"URL":"http:\/\/api.elsevier.com\/content\/article\/PII:S0305900699000070?httpAccept=text\/plain","content-type":"text\/plain","content-version":"vor","intended-application":"text-mining"}],"deposited":{"date-parts":[[2015,9,9]],"date-time":"2015-09-09T06:07:58Z","timestamp":1441778878000},"score":1.0,"issued":{"date-parts":[[1999,10]]},"references-count":0,"alternative-id":["S0305900699000070"],"URL":"http:\/\/dx.doi.org\/10.1016\/s0305-9006(99)00007-0","ISSN":["0305-9006"],"issn-type":[{"value":"0305-9006","type":"print"}],"subject":["Geography,
        Planning and Development"]},{"indexed":{"date-parts":[[2017,10,23]],"date-time":"2017-10-23T19:27:25Z","timestamp":1508786845347},"reference-count":0,"publisher":"Elsevier
        BV","issue":"4","license":[{"URL":"http:\/\/www.elsevier.com\/tdm\/userlicense\/1.0\/","start":{"date-parts":[[1998,12,1]],"date-time":"1998-12-01T00:00:00Z","timestamp":912470400000},"delay-in-days":0,"content-version":"tdm"}],"content-domain":{"domain":[],"crossmark-restriction":false},"short-container-title":["Progress
        in Planning"],"published-print":{"date-parts":[[1998,12]]},"DOI":"10.1016\/s0305-9006(98)00020-8","type":"journal-article","created":{"date-parts":[[2002,7,26]],"date-time":"2002-07-26T00:11:38Z","timestamp":1027642298000},"page":"VI","source":"Crossref","is-referenced-by-count":0,"title":["Preface"],"prefix":"10.1016","volume":"50","author":[{"given":"Maurice","family":"Yeats","affiliation":[]}],"member":"78","container-title":["Progress
        in Planning"],"link":[{"URL":"http:\/\/api.elsevier.com\/content\/article\/PII:S0305900698000208?httpAccept=text\/xml","content-type":"text\/xml","content-version":"vor","intended-application":"text-mining"},{"URL":"http:\/\/api.elsevier.com\/content\/article\/PII:S0305900698000208?httpAccept=text\/plain","content-type":"text\/plain","content-version":"vor","intended-application":"text-mining"}],"deposited":{"date-parts":[[2015,9,9]],"date-time":"2015-09-09T06:07:58Z","timestamp":1441778878000},"score":1.0,"issued":{"date-parts":[[1998,12]]},"references-count":0,"alternative-id":["S0305900698000208"],"URL":"http:\/\/dx.doi.org\/10.1016\/s0305-9006(98)00020-8","ISSN":["0305-9006"],"issn-type":[{"value":"0305-9006","type":"print"}],"subject":["Geography,
        Planning and Development"]},{"indexed":{"date-parts":[[2017,10,23]],"date-time":"2017-10-23T19:27:25Z","timestamp":1508786845389},"reference-count":24,"publisher":"Elsevier
        BV","issue":"1","license":[{"URL":"http:\/\/www.elsevier.com\/tdm\/userlicense\/1.0\/","start":{"date-parts":[[1999,1,1]],"date-time":"1999-01-01T00:00:00Z","timestamp":915148800000},"delay-in-days":0,"content-version":"tdm"}],"content-domain":{"domain":[],"crossmark-restriction":false},"short-container-title":["Powder
        Technology"],"published-print":{"date-parts":[[1999,1]]},"DOI":"10.1016\/s0032-5910(98)00119-3","type":"journal-article","created":{"date-parts":[[2002,7,26]],"date-time":"2002-07-26T00:11:20Z","timestamp":1027642280000},"page":"17-30","source":"Crossref","is-referenced-by-count":0,"title":["Load
        diversion by embedding in crushed salt"],"prefix":"10.1016","volume":"101","author":[{"given":"W.","family":"Feuser","affiliation":[]},{"given":"H.","family":"Vijgen","affiliation":[]},{"given":"E.","family":"Barnert","affiliation":[]}],"member":"78","container-title":["Powder
        Technology"],"link":[{"URL":"http:\/\/api.elsevier.com\/content\/article\/PII:S0032591098001193?httpAccept=text\/xml","content-type":"text\/xml","content-version":"vor","intended-application":"text-mining"},{"URL":"http:\/\/api.elsevier.com\/content\/article\/PII:S0032591098001193?httpAccept=text\/plain","content-type":"text\/plain","content-version":"vor","intended-application":"text-mining"}],"deposited":{"date-parts":[[2017,6,15]],"date-time":"2017-06-15T02:22:06Z","timestamp":1497493326000},"score":1.0,"issued":{"date-parts":[[1999,1]]},"references-count":24,"alternative-id":["S0032591098001193"],"URL":"http:\/\/dx.doi.org\/10.1016\/s0032-5910(98)00119-3","ISSN":["0032-5910"],"issn-type":[{"value":"0032-5910","type":"print"}],"subject":["General
        Chemical Engineering"]}],"items-per-page":3,"query":{"start-index":0,"search-terms":null}}}'
  recorded_at: 2018-04-28 15:12:29 GMT
  recorded_with: vcr/0.0.8.9521, webmockr/0.2.2.9119, crul/0.5.2
```

All components of both the request and response are preserved, so that the HTTP client (in this case `crul`) can reconstruct its own response just as it would if it wasn't using `vcr`.


## vcr enabled testing {#vcr-enabled-testing}

### check vs. test {#check-vs-test}

> TLDR: Run `devtools::test()` before running `devtools::check()`

When running tests or checks of your whole package, note that you'll get different results with
`devtools::check()` vs. `devtools::test()`. This arises because `devtools::check()` runs in a
temporary directory and files created (vcr cassettes) are only in that temporary directory and
thus don't persist after `devtools::check()` exits. 

However, `devtools::test()` does not run in a temporary directory, so files created (vcr
cassettes) are in whatever directory you're running it in.

Alternatively, you can run `devtools::test_file()` to create your vcr cassettes. 

The same goes for using the RStudio IDE buttons/keyboard shortcuts. 

### CRAN {#vcr-enabled-tests-on-cran}

There is no one right answer to how to manage your tests for CRAN. The following is a 
discussion of the various considerations - which should give the reader enough
information to make an educated decision. 

You can run vcr enabled tests on CRAN. CRAN is okay with files associated with tests,
and so in general you can run your vcr enabled tests on CRAN just as you run them
locally.

If you do run your vcr enabled tests on CRAN be aware of a few things:

- If your vcr enabled tests require any environment variables or R options,
they won't be available on CRAN. In these cases you likely want to skip these
tests.
- If your vcr enabled tests have cassettes with sensitive information in them,
you probably do not want to have those cassettes on the internet, in which case
you won't be running vcr enabled tests on CRAN either. In the case of sensitive 
information, you'll want to read the [gitignore cassettes](#gitignore-cassettes)
section

If you are worried at all about problems with vcr enabled tests on CRAN you can use 
`testthat::skip_on_cran()` to skip specific tests.

### CI sites: Travis, Appveyor, etc. {#vcr-ci}

Similar considerations are involved when dealing with Travis, Appveyor, Circle-CI,
etc. 

There are a few differences. With CI services you can manage environment variables
so you can run tests that require API keys, etc. In addition, if tests fail you
aren't threatened with your package being taken down.


