#  (PART) vcr {-}

# Caching HTTP requests {#vcr-intro}

Record HTTP calls and replay them

## Package documentation {#vcr-pkgdown}

Check out <https://docs.ropensci.org/vcr/> for documentation on `vcr` functions.

## Terminology {#terminology}

```{r, results = "asis", echo=FALSE}
get_vcr_doc("man/rmdhunks/glossary.Rmd")
```


## Basic usage {#vcr-basic-usage}

```{r, results = "asis", echo=FALSE}
get_vcr_doc("man/rmdhunks/basic-usage.Rmd")
```

All components of both the request and response are preserved, so that the HTTP client (in this case `crul`) can reconstruct its own response just as it would if it wasn't using `vcr`.

## vcr enabled testing {#vcr-enabled-testing}

### check vs. test {#check-vs-test}

> TLDR: Run `devtools::test()` before running `devtools::check()` for recording your cassettes.

When running tests or checks of your whole package, note that you'll get different results with
`devtools::check()` (check button of RStudio build pane) vs. `devtools::test()` (test button of RStudio build pane). This arises because `devtools::check()` runs in a
temporary directory and files created (vcr cassettes) are only in that temporary directory and
thus don't persist after `devtools::check()` exits. 

However, `devtools::test()` does not run in a temporary directory, so files created (vcr
cassettes) are in whatever directory you're running it in.

Alternatively, you can run `devtools::test_file()` (or the "Run test" button in RStudio) to create your vcr cassettes one test file at a time. 


### CI sites: GitHub Actions, Appveyor, etc. {#vcr-ci}

Refer to [the security chapter](#security-chapter)