```{r echo = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

# vcr configuration {#vcr-configuration}

`vcr` configuration

```{r}
library("vcr")
```

## Get your configuration

Use `vcr_configuration()` to get the current configuration

```{r }
vcr_configuration()
```

You can get the default configuration variables via `vcr_config_defaults()`

```{r}
vcr_config_defaults()
```

These defaults are set when you load `vcr` - you can override any of them as described below.

## Set configuration variables

Use `vcr_configure()` to set configuration variables.

For example, set a single variable:

```{r}
vcr_configure(
  dir = "foobar/vcr_cassettes"
)
```

Or many at once:

```{r}
vcr_configure(
  dir = "foobar/vcr_cassettes",
  record = "all"
)
```

## Re-set to defaults {#config-reset}

```{r}
vcr_configure_reset()
```

## dir - directory of where cassettes are stored {#config-dir}

```{r}
vcr_configure(dir = "new/path")
```

## record - record mode {#config-record-mode}

One of: 'all', 'none', 'new_episodes', 'once'. See `?recording` for info on the options

```{r}
vcr_configure(record = "new_episodes")
```

## match_requests_on - customize how vcr matches requests {#config-match-on}

```{r}
vcr_configure(match_requests_on = c('query', 'headers'))
```

## allow_unused_http_interactions - Allow HTTP connections when no cassette {#config-allow-unused}

Default is `TRUE`, and thus does not error when http interactions are unused. You 
can set to `FALSE` in which case vcr errors when a cassette is ejected and 
not all http interactions have been used.

```{r}
vcr_configure(allow_unused_http_interactions = FALSE)
```

## serialize_with - which serializer to use {#config-serialize-with}

Right now the only option is `yaml`

```{r}
vcr_configure(serialize_with = "yaml")
```

## persist_with - which persister to use {#config-persist-with}

Right now the only option is `FileSystem`

```{r}
vcr_configure(persist_with = "FileSystem")
```

## ignore requests  {#config-ignore-requests}

### ignore_hosts - specify particular hosts to ignore

```{r}
vcr_configure(ignore_hosts = "google.com")
```

### ignore_localhost - ignore all localhost flavors

```{r}
vcr_configure(ignore_localhost = TRUE)
```

### ignore_request - ignore any request for which function is true

```{r}
vcr_configure(ignore_request = function(x) x == 5)
```

## uri_parser - which uri parser to use {#config-uri-parser}

By default we use `httr::parse_url`, but you can use a different one. Remember 
to pass in the function quoted, and namespaced.

```{r}
vcr_configure(uri_parser = "urltools::url_parse")
```

## preserve_exact_body_bytes {#config-preserve-exact-body-bytes}

Some HTTP servers are not well-behaved and respond with invalid data. Set 
`preserve_exact_body_bytes` to `TRUE` to base64 encode the result body in 
order to preserve the bytes exactly as-is. `vcr` does not do this by
default, since base64-encoding the string removes the human readibility 
of the cassette.

```{r}
vcr_configure(preserve_exact_body_bytes = TRUE)
```

## allow_http_connections_when_no_cassette {#allow-http-connections-when-no-cassette}

Determines how `vcr` treats HTTP requests that are made when no cassette is in use. 
When `TRUE`, requests made when there is no vcr cassette in use will be allowed.
When `FALSE` (default), an [UnhandledHTTPRequestError] error will be raised for 
any HTTP request made when there is no cassette in use

```{r}
vcr_configure(allow_http_connections_when_no_cassette = TRUE)
```


```{r echo=FALSE}
vcr_configure_reset()
```

## write_disk_path {#write-disk-path}

The path to write files to for any requests that write responses to disk.
By default this parameter is `NULL`; if you don't set this and you do http 
requests while using vcr, you'll get an error that you need to set this config
variable (or you may just get an invalid path error).

For testing a package, you'll probably want this path to be in your `tests/`
directory, perhaps next to your cassettes directory, e.g., if your cassettes
are in `tests/fixtures`, then put your files from requests that write to disk
in `tests/files`. Note: in the below example, `vcr_configure` is run from 
within `tests/testthat`, so you set the paths relative to that location.

```{r}
vcr_configure(dir = "../fixtures", write_disk_path = "../files")
```

If you want to ignore these files in your installed package, 
add them to `.Rinstignore`. If you want these files ignored on build
then add them to `.Rbuildignore`. However, adding these files to `.Rbuildignore`
will make tests that depend on these files break because the files won't be found; so
you'll likely have to skip the associated tests as well. 
