#  (PART) introduction {-}

# HTTP in R 101

## What is HTTP?

HTTP means HyperText Transport Protocol, but you were probably not just looking for a translation of the abbreviation.
HTTP is a way for you to exchange information with a remote server.
In your package, if information is going back and forth between the R session and internet, you are using some sort of HTTP tooling.
Your package is making _requests_ and receives _responses_.

### HTTP requests

The HTTP request is what your package makes.
It has a method (are you fetching information via `GET`? are you sending information via `POST`?), different parts of an URL (domain, endpoint, query string), headers (containing e.g. your secret identifiers).
It can contain a body, for instance you might be sending data as JSON. 
In that case one of the header will describe the content.

How do you know what request to make from your package?
Hopefully you are interacting with a well documented web resource that will explain to you what methods are associated with what endpoints.

### HTTP responses

The HTTP response is what the remote server provides, and what your package parses.
A response has a status code indicating whether the request succeeded, response headers, and (optionally) a response body.

Hopefully the documentation of the web API or web resource you are working with shows good examples of responses.
In any case you'll find yourself experimenting with different requests to see what the response "looks like".

### More resources about HTTP

How do you get started with interacting with HTTP in R?

#### General HTTP resources

* [Mozilla Developer Network docs about HTTP](https://developer.mozilla.org/en-US/docs/Web/HTTP) (recommended in the zine mentioned thereafter)
* (_not free_) [Julia Evans' Zine "HTTP: Learn your browser's language!"](https://wizardzines.com/zines/http/) 
* The docs of the web API you are aiming to work with, and a search engine to understand the words that are new.

### HTTP with R

* The docs of the R package you end up choosing!
* Digging into the source code of another package that does similar things.


## HTTP requests in R: what package?

In R, to interact with web resources, it is recommended to use `{curl}`; or its higher-level interfaces `{httr}` ([pronounced _hitter_ or _h-t-t-r_](https://community.rstudio.com/t/pronunciations-of-common-r-terms/1810/15)) or `{crul}`.

Do not use RCurl, because it is not actively maintained!

When writing a package interacting with web resources, you will probably use either `{httr}` or `{crul}`.

* httr is the most popular and oldest of the two, and supports OAuth. 
httr docs feature a vignette called [Best practices for API packages](https://httr.r-lib.org/articles/api-packages.html)

* crul does not support OAuth but it uses an object-oriented interface, which you might like.
crul has a set of [clients, or ways to perform requests](https://docs.ropensci.org/crul/articles/choosing-a-client.html), that might be handy. crul also has a vignette about [API package best practices
](https://docs.ropensci.org/crul/articles/best-practices-api-packages.html).

Below we will try to programmatically access the [status of GitHub](https://www.githubstatus.com/api/#status), the open-source platfrom provided by the company of the same name.
We will access the same information with httr and crul.
If you decide for the low-level curl, feel free to contribute an example.

```{r}
github_url <- "https://kctbh9vrtdwd.statuspage.io/api/v2/status.json"
```

The URL above leaves no doubt as to what format the data is provided in, JSON!

Let's first use httr.

```{r}
response <- httr::GET(github_url)

# Check the response status
httr::http_status(response)

# Or in a package you'd just write
httr::stop_for_status(response)

# Parse the content
httr::content(response)

# In case you wonder, the format was obtained from a header
httr::headers(response)$`content-type`
```

Now, the same with crul.

```{r}
# Create a client and get a response
client <- crul::HttpClient$new(github_url)
response <- client$get()


# Check the response status
response$status_http()

# Or in a package you'd just write
response$raise_for_status()

# Parse the content
response$parse()
jsonlite::fromJSON(response$parse())
```

Hopefully these very short snippets give you an idea of what syntax to expect when choosing one of those packages.

Note that the choice of a package will constrain the HTTP testing tools you can use.
However, the general ideas will remain the same.
You could switch your package backend from say crul to httr _without changing your tests_, if your tests do not test too many specifities of internals.